sWGS validation report

### 2019-08-20 Paper.Rmd
...

ds.preds = read_tsv(paste0(dir, '/downsampled_preds.tsv'), col_types = cols(
  Sample = col_character(),
  Probability = col_double(),
  `Relative Risk` = col_double(),
  Risk = col_character(),
  PatientID = col_character(),
  Status = col_character(),
  Tissue = col_character(),
  `Expected Risk` = col_character(),
  Grade_patient = col_character(),
  Grade_biopsy = col_character(),
  Study = col_character(),
  Type = col_character(),
  Endoscopy = col_date(format = "")
))

>>>>

ds.preds = do.call(bind_rows, purrr::map(list.files(dir, 'predictions', recursive=T, full.names=T), function(f) {
  read_tsv(f, col_types = cols(
  Sample = col_character(),
  Probability = col_double(),
  `Relative Risk` = col_double(),
  Risk = col_character(),
  PatientID = col_character(),
  Status = col_character(),
  Tissue = col_character(),
  `Expected Risk` = col_character(),
  Grade_patient = col_character(),
  Grade_biopsy = col_character(),
  Study = col_character(),
  Type = col_character(),
  Endoscopy = col_date(format = "") ))
}))

### 2019-08-20 Validation Report.Rmd
...

pred.dir = '~/Data/BarrettsProgressionRisk/Analysis/validation/predictions'

@@

all.val %>% filter(!Samplename %in% val$sample )

val = val %>% filter(sample %in% (all.val %>% dplyr::select(Samplename) %>% pull) ) %>% 
          left_join( all.val, val %>% mutate(sample = str_replace(sample, '_', '-')), by=c('sample'='Samplename'))

@@

# Quick Summary

@@

val %>% dplyr::group_by(Batch) %>% dplyr::summarise( Pass = length(which(varMAD_median <= qc.cutoff)), Fail = length(which(varMAD_median > qc.cutoff))  ) %>% kable(caption = 'Number of samples per batch that pass/fail') %>% kable_styling('striped', full_width = F)

@@

# New processing

@@

on = left_join(val %>% ungroup %>% filter(Batch %in% c(8)),
               readxl::read_xlsx(val.file, sheet='Batch 8') %>% dplyr::select(`Block ID`, `Endoscopy`, `Sample Type`))

@@

batch8_preds = do.call(bind_rows,
  purrr::map(grep( paste(unique(on$`Patient ID`), collapse='|'), list.files(preds.dir, full.names = T, recursive = T), value=T), function(f) {
             read_tsv(f, col_types = cols(
                Sample = col_character(),
                Probability = col_double(),
                `Relative Risk` = col_double(),
                Risk = col_character(),
                `Hospital Research ID` = col_character(),
                `Block ID` = col_character(),
                Endoscopy = col_date(format = ""),
                Pathology = col_character(),
                `SLX-ID` = col_character(),
                `Index Sequence` = col_character(),
                `Path Notes` = col_logical()
      ))
})) %>% dplyr::mutate_if(is.numeric, list(round), 2)

batch8_preds %>% dplyr::select(`Hospital Research ID`, Sample, everything(), -matches('SLX|Index') ) %>% kable() %>% kable_styling('striped')

@@

```{r, fig.height=8}

@@

>>>>

@@

#all.val %>% filter(!Samplename %in% val$sample )

val = val %>% filter(sample %in% (all.val %>% dplyr::select(Samplename) %>% pull) ) %>% 
          left_join( all.val, val %>% mutate(sample = str_replace(sample, '_', '-')), by=c('sample'='Samplename')) %>% unique

@@

# Quick QC Summary

@@

val %>% dplyr::group_by(Batch) %>% dplyr::summarise( Pass = length(which(varMAD_median <= qc.cutoff)), Fail = length(which(varMAD_median > qc.cutoff))  ) %>% kable(caption = 'Number of samples per batch that pass/fail') %>% kable_styling('striped', full_width = F)
```

@@

# New Validation Cohorts

@@

```{r}
on = left_join(val %>% ungroup %>% filter(Batch == 8),
               readxl::read_xlsx(val.file, sheet='Batch 8') %>% dplyr::select(`Block ID`, `Endoscopy`, `Sample Type`, `Index Sequence`),
               by=c('Block ID','Sample Type', 'Index Sequence')) %>% 
  arrange(`Patient ID`, sample)

@@

batch8_preds = do.call(bind_rows,
  purrr::map(grep( paste(unique(on$`Patient ID`), collapse='|'), list.files(preds.dir, full.names = T, recursive = T), value=T), function(f) {
             read_tsv(f, col_types = cols(
                Sample = col_character(),
                Probability = col_double(),
                `Relative Risk` = col_double(),
                Risk = col_character(),
                `Hospital Research ID` = col_character(),
                `Block ID` = col_character(),
                Endoscopy = col_date(format = ""),
                Pathology = col_character(),
                `SLX-ID` = col_character(),
                `Index Sequence` = col_character(),
                `Path Notes` = col_character()
      ))
})) %>% dplyr::mutate_if(is.numeric, list(round), 2)

batch8_preds = left_join(batch8_preds,on %>% dplyr::select(sample, `Sample Type`, Age), by=c('Sample'='sample'))

batch8_preds %>% dplyr::select(`Hospital Research ID`, Sample, everything(), -matches('SLX|Index') ) %>% arrange(`Hospital Research ID`, `Sample Type`) %>% kable() %>% kable_styling('striped')

@@

```{r, fig.height=8, eval=F}

@@

```{r echo=F, eval=F}
dir = '~/Data/BarrettsProgressionRisk/Analysis/downsampled/predictions/0.9'
info = readxl::read_xlsx('~/Data/BarrettsProgressionRisk/QDNAseq/all_downsampled/downsampled_ids.xlsx')

ds.preds = do.call(bind_rows, purrr::map(list.files(dir, 'predictions', recursive=T, full.names=T), function(f) {
  read_tsv(f, col_types = cols(
  Sample = col_character(),
  Probability = col_double(),
  `Relative Risk` = col_double(),
  Risk = col_character(),
  PatientID = col_character(),
  Status = col_character(),
  Tissue = col_character(),
  `Expected Risk` = col_character(),
  Grade_patient = col_character(),
  Grade_biopsy = col_character(),
  Study = col_character(),
  Type = col_character(),
  Endoscopy = col_date(format = "") ))
}))

## TODO merge in RR from 'back'

ds.preds = ds.preds %>% dplyr::select(-Status) %>% left_join(info %>% dplyr::select(`Illumina ID`, Status), by=c('Sample' = 'Illumina ID')) %>% dplyr::mutate(Type = factor(Type, levels=c('Normal','NDBE', 'LGD', 'Tumor Adjacent BE'))) %>% arrange(Probability)

 m = reshape2::melt(ds.preds, measure.vars = c('Relative Risk'), id.vars = c('Type', 'Status', 'Risk'))

pr = ggplot(m, aes(variable, value)) + 
  facet_grid(~Type, scales = 'free_x') + 
  geom_boxplot(aes(group=variable, fill=Type), outlier.colour = NA, show.legend = F) + 
  geom_jitter(width=0.2, aes(shape=Status, color=Risk), size=2, show.legend = F) + 
  scale_color_manual(values =  BarrettsProgressionRisk::riskColors()) +
  #scale_color_gradientn(colors = myPal,  name='') +
  scale_fill_manual(values=rev(RColorBrewer::brewer.pal(5,'RdYlBu')[c(1,2,4,5)])) +
  labs(x='', y='Relative Risk', title='Predictions on downsampled patients') + plot.theme +
  theme(axis.text.x = element_text(angle=45, hjust=1))
pr

ds.preds %>% dplyr::group_by(Status, Risk) %>% dplyr::summarise(n=length(Risk)) %>% spread(Risk, n) %>% kableExtra::kable(caption = 'Sample by risk and known status') %>% kableExtra::kable_styling(full_width = F)
